FraCaS: Temporal Analysis

### 2020-11-08 paper2020/paper.tex
minor

\begin{abstract}
  In this paper, we propose an implementation of temporal semantics
  which is suitable for inference problems. This implementation
  translates syntax trees to logical formulas, suitable for
  consumption by the Coq proof assistant. We support several phenomena
  including: temporal references, temporal adverbs, aspectual classes
  and progressives.  We apply these semantics to temporal problems of
  the FraCaS testsuite and obtain an accuracy of 71 percent.
\end{abstract}

@@

The semantics of tense and aspect has been a long standing issue in
the study of formal semantics since the early days of Montague Grammar
and a number of different ideas have been put forth on the table to
deal with them throughout the years. Recent proposals include the
works of the following authors:
\citet{dowty:2012,prior:2003,steedman_productions_2000,higginbotham:2009,fernando:2015}.
%
The
semantics of tense and aspect have been also considered in the study of
Natural Language Inference (NLI). The various datasets
for NLI that have been proposed by the years contain examples that
have some implicit or explicit reliance on inferences related to tense
and aspect. One of the early datasets used to test logical approaches,
the FraCaS test suite~\citep{cooper:1996} contains a whole section
dedicated to temporal and aspectual inference (section 7 of the dataset). This part
of the FraCaS test suite has been difficult to tackle. That is,
so far, no computational system has been capable to deal with it in its entirety: when
authors report accuracy over the FraCaS test suite they
skip this section.
%
In fact, they also often skip the anaphora and ellipsis sections, the
exception being the system presented by
\citet{bernardy_type-theoretical_2017,bernardy_wide-coverage_2019},
which includes support for anaphora and ellipsis but still omit the
temporal section.\jp{check todo in footnote}\footnote{One can consider that \citet{maccartney:2007} have made a run against the whole test suite. However, they do not deal with multi-premise cases. Consequently only 36/75 cases in the temporal section are treated{TODO: jp: treated or attempted? I suppose attempted (otherwise .61 accuracy makes no sense)}. The general accuracy of the system is .59, and .61 for the temporal section. Our system, as shown \cref{tab:results}, presents considerable improvements in coverage and accuracy over that of \citeauthor{maccartney:2007}.}
%
In this paper, we take up the challenge of providing a
computationally viable account of tense and aspect to deal with the
  section 7 of the FraCaS test suite. Our account is not meant
to be a theoretically extensive account of tense and aspect, but rather an
account that is driven by the need to cover the test suite in a way
that is general enough to capture the test suite examples, \emph{while still covering the rest of the FraCaS test suite}.
%

>>>>

\begin{abstract}
  In this paper, we propose an implementation of temporal semantics
  which is suitable for inference problems. This implementation
  translates syntax trees to logical formulas, suitable for
  consumption by the Coq proof assistant. We support several phenomena
  including: temporal references, temporal adverbs, aspectual classes
  and progressives.  We apply these semantics to temporal problems of
  the FraCaS testsuite and obtain an accuracy of 81 percent.
\end{abstract}

@@

The semantics of tense and aspect has been a long standing issue in
the study of formal semantics since the early days of Montague Grammar
and a number of different ideas have been put forth on the table to
deal with them throughout the years. Recent proposals include the
works of the following authors:
\citet{dowty:2012,prior:2003,steedman_productions_2000,higginbotham:2009,fernando:2015}.
%
The
semantics of tense and aspect have been also considered in the study of
Natural Language Inference (NLI). The various datasets
for NLI that have been proposed by the years contain examples that
have some implicit or explicit reliance on inferences related to tense
and aspect. One of the early datasets used to test logical approaches,
the FraCaS test suite~\citep{cooper:1996} contains a whole section
dedicated to temporal and aspectual inference (section 7 of the dataset). This part
of the FraCaS test suite has been difficult to tackle. That is,
so far, no computational system has been capable to deal with it in its entirety: when
authors report accuracy over the FraCaS test suite they
skip this section.
%
In fact, they also often skip the anaphora and ellipsis sections, the
exception being the system presented by
\citet{bernardy_type-theoretical_2017,bernardy_wide-coverage_2019},
which includes support for anaphora and ellipsis but still omit the
temporal section.\jp{check todo in footnote}\footnote{One can consider that \citet{maccartney:2007} have made a run against the whole test suite. However, they do not deal with multi-premise cases. Consequently only 36/75 cases in the temporal section are attempted. The general accuracy of the system is .59, and .61 for the temporal section. Our system, as shown \cref{tab:results}, presents considerable improvements in coverage and accuracy over that of \citeauthor{maccartney:2007}.}
%
In this paper, we take up the challenge of providing a
computationally viable account of tense and aspect to deal with the
  section 7 of the FraCaS test suite. Our account is not meant
to be a theoretically extensive account of tense and aspect, but rather an
account that is driven by the need to cover the test suite in a way
that is general enough to capture the test suite examples, \emph{while still covering the rest of the FraCaS test suite}.
%
